---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# flavorlinguist

<!-- badges: start -->
<!-- badges: end -->

The goal of the flavorlinguist package is to provide a streamlined, low-overhead, low barrier to entry set of tools for preprocessing natural language flavor descriptions into tidy data that's ready for analysis.

Many larger libraries for lemmatizing, annotating, and filtering natural language tokens are not stable, use a lot of computing space and power, and most importantly, don't perform very well on flavor descriptions because they're not a large part of the training set.

The tools in this package are configured to give you a common sense, expected set of word counts at the most basic, but they're presented in a modular form that allows you to combine them with other libraries when necessary for your goals.

## Installation

You can install the development version of flavorlinguist from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("lhami/flavorlinguist")
```

## Example

This package is a work-in-progress. For now, the first function to be implemented is `get_root()`, which takes a vector of (ideally pre-lemmatized) tokens and spits out their adjective forms.

```{r example}
library(flavorlinguist)
x <- c("tart", "tartness", "tarts", "fruit", "fruity", "fruitiness", "fruits",
"whiskey", "whisky", "nuts", "nut", "nutty", "rotten", "rotted", "rot",
"peppery", "plummy", "cheese", "cheesy")
get_root(x)
```
